---
title: "Reproducible Templates for Analysis final"
author: "Author: Christian Ruiz"
date: "`r format(Sys.Date(), '%A, %B, %d, %Y')`"
output: 
  html_document:
    theme: cerulean
    higlight: kate
    toc: true
    toc_float: true

---

# Setup
```{r, echo=FALSE, message=FALSE, warning=FALSE }
knitr::read_chunk("code/setup.R")
```

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
```

# Summary
```{r, child = "text/summarySection.Rmd"}

```


# Section of three or more bulleted items

**Here is a numbered list of items covered in the course**

1. Week 1
    a. Introduction to reproducible research and dynamic documentation
        i. History of literate programming
        ii. Opening and using github account
    
2. Week 2
    a. Rmarkdown syntax
        i. Formating rmarkdown documents
        ii. changing appearances via yaml header and or css file
        iii. bookdown

3. Week 3
    a. Rmarkdown templates
        i. Implemented parameters
        ii. Covered 538 package for datasets
    
4. Week 4
    a. Leveraging custom templates from leading scientific journals
        i. Tufte style
        ii. How to make packages
    
5. Week 5
    a. Working on teams and disseminating research
        i. Modularized rmarkdown template design making
        ii. Sharing templates online at Rpubs
        iii. Flexboard


# Plot of pressure dataset

```{r}
plot(pressure)
```

# Table of cars dataset

```{r}

knitr::kable(head(cars), caption = "Top 6 rows of cars dataset") %>% 
  kable_styling("striped", "bordered")

```

